Our Title

### 2015-04-30 draft.tex
Edits incorporated from James, Julie, the non-linear logic tree, Nick& Chris' fuel cycle section, and Julie's draft scoping section.
Changed paragraph and line spacing.
Corrected some ISIS / ISIL consistancy.

\setlength\parindent{0pt}
\setlength\parskip{1.2ex}

@@

\subsection{How does this relate to their potential nuclear interests?}
\subsubsection{????? Missing ?????}

\subsubsection{????Move in info from mat / signatures group????}

@@

ISIS taking over a major hospital/university - this is a major concern for chem/bio, I think, but not sure if there is a nuclear component. I know that for DoD, terrorist control of failed state capabilities (in the form of former/current facilities) for WMD purposes is a top concern.

Agency cooperation to manage and coordinate a crisis. This would include current actions to prepare to respond to a crisis, and might have lessons learned from Fukushima and Ebola in terms of interagency action. How do we utilize agencies and individuals without access to top secret information in the event of a loose nuke? There will be a lot of expertise that could help but intel community and white house won't want broad knowledge that ISIS may be getting close to nuclear device.

This goes along with planning and preparing for a situation with a considerable lack of uncertainty. We're not just planning what to do, but planning structures that allow us to respond quickly to uncertainty. Looking for a lost nuke or lost nuclear material is like looking for a needle in a haystack. Since there is never a precise enough tool to find it, how do we shrink the haystack? How do we ensure we're leveraging collective knowledge of various agencies to zero in on it and verify if it's ISIS who has it. Even if we're keeping an eye on ISIS, are we developing capabilities for the event of a lost nuke (or whatever), to look and investigate, is there any way this thing is making its way to ISIS?

@@

There is significant competition within DoD over ISR (intelligence, surveillance, recognizance). How do we make sure the counterterrorism/WMD office gets enough of it to monitor nuclear materials in countries with ISIS sympathizers, and if we don't get it, what's the back up plan?

Broadly speaking, working this problem without assuming false precision. We don't want to assume we'll know exactly what ISIS has or where things are going, etc.

@@

Information sharing in the international IC is immensely more complicated than between internal U.S. agencies. The mere fact of declared opposition to ISIS is an insufficient basis for intelligence sharing alone.  Indeed, the U.S. various strained relationships with many allies in the fight against ISIL. It is assumed that information sharing on the ISIL issue would fall along lines consistent with historical cooperation levels. Cooperation levels can be divided into a simple system of three levels as shown in \autoref{tab:relation_table}.

>>>>

\setlength\parindent{0pt}
\setlength\parskip{1.5ex}

@@

\subsection{How does this relate to their potential nuclear interests?}
\subsubsection{????? Missing ?????}
\subsubsection{????Move in info from mat / signatures group????}

@@

ISIL taking over a major hospital/university - this is a major concern for chem/bio, I think, but not sure if there is a nuclear component. I know that for DoD, terrorist control of failed state capabilities (in the form of former/current facilities) for WMD purposes is a top concern.

Agency cooperation to manage and coordinate a crisis. This would include current actions to prepare to respond to a crisis, and might have lessons learned from Fukushima and Ebola in terms of interagency action. How do we utilize agencies and individuals without access to top secret information in the event of a loose nuke? There will be a lot of expertise that could help but intel community and white house won't want broad knowledge that ISIL may be getting close to nuclear device.

This goes along with planning and preparing for a situation with a considerable lack of uncertainty. We're not just planning what to do, but planning structures that allow us to respond quickly to uncertainty. Looking for a lost nuke or lost nuclear material is like looking for a needle in a haystack. Since there is never a precise enough tool to find it, how do we shrink the haystack? How do we ensure we're leveraging collective knowledge of various agencies to zero in on it and verify if it's ISIL who has it. Even if we're keeping an eye on ISIL, are we developing capabilities for the event of a lost nuke (or whatever), to look and investigate, is there any way this thing is making its way to ISIL?

@@

There is significant competition within DoD over ISR (intelligence, surveillance, recognizance). How do we make sure the counterterrorism/WMD office gets enough of it to monitor nuclear materials in countries with ISIL sympathizers, and if we don't get it, what's the back up plan?

Broadly speaking, working this problem without assuming false precision. We don't want to assume we'll know exactly what ISIL has or where things are going, etc.

@@

Information sharing in the international IC is immensely more complicated than between internal U.S. agencies. The mere fact of declared opposition to ISIL is an insufficient basis for intelligence sharing alone.  Indeed, the U.S. various strained relationships with many allies in the fight against ISIL. It is assumed that information sharing on the ISIL issue would fall along lines consistent with historical cooperation levels. Cooperation levels can be divided into a simple system of three levels as shown in \autoref{tab:relation_table}.
